sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2019-09-11 inst/documents/rotations_notes.Rmd
fix docs

in_expt
in_runs

@@

~ investigate getting runs to name the output file with the date 
~ and create a similarly named metadata file that records run input params 
~ think about moving run control from a rmd to a .R script
~ think about being able to create named run inputs files (csv ?) that store the list of inputs (can be the same one that is saved as run metadata)

>>>>

# 6/9/19

GOOD getting there, now a csv file saved in extdata that specifies the experiment

linputs_multi <- set_run_inputs()
# to get all inputs for a single scenario
linputs <- purrr::map(linputs_multi, 2)
# run one scenario
dfres <- do.call(run_rot, linputs)

# 10/9/19
got different insecticides working
added get_one_in() to get inputs for one scenario from multi-senario file

# 11/09/19

This is the new workflow.

# read an experiment file specifying ranges
inex <- read_in_expt() #specify filename
# create an object containing inputs for all scenarios
linmulti <- set_run_inputs(inex=inex)
# get inputs for a single scenario
linputs <- get_one_in(linmulti, scen_num=2)
# run one scenario
dfres <- do.call(run_rot, linputs)

@@

~ add option for different insecticides to the experiment file

~ add the random seed to the experiment file (and decide where it will be set)

~ investigate getting runs to name the output file with the date 
~ and create a similarly named metadata file that records run input params 
~ think about moving run control from a rmd to a .R script
